Temperature Measurements in Optical Tweezer Experiments

### 2017-01-09 doc/draft1.tex
added while loop, renders

\newpage
\section{Results}
% results with different parameters, graphs, etc.
Since the simulation consists of various parts that have to work together, we first need to check if every part itself works.\\
The first element of the simulation is the setup of the FCC lattice on which the particles are placed on. To check if this is done correctly, we can
use a visualisation and rendering software such as VMD\cite{Humphrey1996} or OVITO\cite{Stukowski2010}. The rendered image of the nano crystal can be
seen in fig.~\ref{fig:glass}.
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.2]{images/initial_position_red.png}
        \caption{}
        \label{fig:gascube}
    \end{center}
\end{figure}

>>>>

\newpage
\section{Results}
% results with different parameters, graphs, etc.
Since the simulation consists of various parts that have to work together, we first need to check if every part itself works.\\
\subsection{The Crystal}
The first element of the simulation is the setup of the FCC lattice on which the particles are placed on. To check if this is done correctly, we can
use a visualisation and rendering software such as VMD\cite{Humphrey1996} or OVITO\cite{Stukowski2010}. The rendered image of the nano crystal 
can be seen in fig.~\ref{fig:glass}. The chosen perspective shows the structure of the FCC lattice, where 3 layers are forming 
where the atoms take the position on the gap between the atoms from the layer below.\\
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.2]{images/fcc_rendering_new.png}
        \caption{Rendering of the model of the nano crystal before starting the simulation. 
                    The perspective shows the 3 layers of the FCC lattice. These layers consist of atoms
                    taking the position above the gap between two of the atoms from the layer below and match the positions of the atoms 2 layers
                below. The black box is the outline of the particles' positions and shows the geometry of the system.}
        \label{fig:glass}
    \end{center}
\end{figure}
